### 2015-08-10 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/AxiSEM_modif_for_coupling_with_specfem/MANUAL/virtual_box_tutorial.tex
Clean NEW Axisem DIR

* Tarje:
Hi Kasra, on a quick look, this seems excellent, but from my experience it’s better to have a very easy and quick first run of the tasks, e.g. on ONE page with all the important calls and major points we wish to achieve... and delegate images and details to an appendix. So, let’s keep all this in but reshuffle it to have a concise early section. Tarje

@@

(TAS÷
1) Load data from one of the 5 events (Kasra) with Obspy, plot cross sections
2) change AxiSEM input parameters to run this scenario, submit job
3) check mesh, background model, source-receiver geometry (google earth)
4) run post processing, filter, sum, movie snapshots
5) Movie snapshots
6) plot data vs. synthetics
7) plot AxiSEM synthetics vs SPECFEM
8) change input parameters (source CMT), load run with different background model

>>>>

* Tarje:
Hi Kasra, on a quick look, this seems excellent, but from my experience it's better to have a very easy and quick first run of the tasks, e.g. on ONE page with all the important calls and major points we wish to achieve... and delegate images and details to an appendix. So, let's keep all this in but reshuffle it to have a concise early section. Tarje

@@

(TAS?
1) Load data from one of the 5 events (Kasra) with Obspy, plot cross sections
2) change AxiSEM input parameters to run this scenario, submit job
3) check mesh, background model, source-receiver geometry (google earth)
4) run post processing, filter, sum, movie snapshots
5) Movie snapshots
6) plot data vs. synthetics
7) plot AxiSEM synthetics vs SPECFEM
8) change input parameters (source CMT), load run with different background model
